\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{A Radial Time Projection Chamber for $\alpha$ detection in CLAS at JLab}

### 2017-10-17 eg6-letters/NIM/review-1/review-1.tex
added the answers for the last 25 questions

\section*{Reviewers' comments (11 Oct 2017)}

@@

Summary: the article describes the layout, operation and performances of a Radial Time Projection Chamber with the electron amplification stage provided by three layers of GEM. The main novelty is the application of the electron multiplier for the amplification stage in a TPC on a semi-cylindrical shaped plane. The detector, originally built for the BoNuS experiment, is in fact formed by two semi-cylindrically shaped halves connected together, with the axis coincident with the beam line. 
The detector was implemented to measure DVCS of electrons on different light nuclei and the performances were evaluated on electron - 4He elastic scattering runs.
Chapter 1 describes the CLAS @ JLab detector, inside which the RTPC was installed and took data. 
Chapter 2 focuses on the RTPC mechanical and electrical layout. From inner to outer, there are: the 4He gas target, a 4He gas gap, the actual time projection chamber. The time projection chamber is a 200 long detector composed by different gas gaps limited by concentric electrodes around the axis: cathode (R=30mm), G1(R=60mm), G2(R=63mm), G3(R=66mm), readout plane (R=69mm). Everything fits inside a 5T solenoidal magnetic field. It provides both time and charge measurements.
Chapter 3 is a short description of the electronics and readout, mainly inherited from ALICE and BoNuS. The improvement stands in the higher readout rate capability.
Chapter 4 talks about calibration of drift velocity, drift paths and energy loss measurements by the usage of simulations with MAGBOLTZ and tuning the results on elastic scattering data.
Chapter 5 concentrates on track finding/fitting procedure and noise evaluation and subtraction.
Chapter 6 reports on resolution and efficiency from the elastic scattering reconstruction of 2 GeV electrons on 4He and Chapter 7 concludes the paper.

The article main points of interest are the followings:\\
a)  the usage of GEMs as avalanche creators inside the time projection chamber. As far as I know other TPC with the wires substituted by GEM layers have been (or are being) realized, like ALICE TPC upgrade or the FOPI one (proposed for PANDA), but in those cases the GEM are planar and on the end plane of the TPC, not around the beamline.\\
b) The shaping of the GEM foils around the target. However, since now a fully cylindrical GEM foil has been realized (for the KLOE-2 detector and for the next BESIII inner tracker) I would not call these "cylindrical" GEMs, but "semi-cylindrical" GEMs to point out the difference (which reflects in the construction procedure).\\
Maybe these other experiments using GEMs should be mentioned due to the similarities, thought they are successive in time to this RTPC construction.
Concerning the work description, it is mainly exhaustive, but in some points there are open questions that I would like to submit to the authors in the following.
--------------------------------------------------

\section*{Chapter by chapter comments}:

@@

\subsection*{Chapter 2}
\item As already said I would not speak of cylindrical GEMs but semi-cylindrical. Moreover, please add the reference to Sauli's paper [11] when speaking the first time about GEM in the text.
\textcolor{blue}{ }

\item In my opinion, this chapter should highlight better which are the improvements w.r.t. BoNuS detector to underline the originality of this work. For example, better acceptance? Higher gain? Higher electric stability? Lower material budget? Please quote some old and new values, maybe in a table, to make them evident.
\textcolor{blue}{ }

\item Relevant length and thicknesses of the various elements are reported in the text and in the figure, can you please add also the z position of the target w.r.t the detector? To give the complete information, I would also add the value of the induction gap electric field, which is the only missing field value and the value of the reached amplification gain with the three GEM.
\textcolor{blue}{ }

\item When speaking of low spark rate the reference [12] is quoted, which is the PDG. Maybe it is better to quote more specific studies like the ones by Bachmann et al.
\textcolor{blue}{ }

\item line 119: is the Kapton of the GEM foil really 300 mum thick? It is usually very thin, like 50 mum, in order to have low material budget and very high fields.
\textcolor{blue}{ }

\subsection*{ Chapter 3}
\item The description of the electronics looks to me a little not well organized, like a collection of info from previous descriptions from ALICE and BoNuS. It is a series of details, some of which not really relevant for the good understanding of the work described in the paper. So, I would put only some general info (the number of channels/pad, the number of time samples and their width for each channel and the number of  ADC samples and their width for each channel) with the reference where to find more material and just write explicitly the novelties, such as the fact that the acquisition rate was increased (footnote 2).
\textcolor{blue}{ }

\item Also, I understand that fig. 5 comes from reference [14], updated with the values of the RTPC instead of the ALICE-TPC, but it seems to me that there are some parts of the picture which have to be fixed. I list them here:
- why does it say 768 pads?
- why 7.6 microsec?
- the anode wire e grid make no sense here
- why L1 and L2 (trigger levels?) 
\textcolor{blue}{ }

\subsection*{ Chapter 4}
	/paragraph 4.1
\item I would really prefer to call it drift "velocity" instead of drift "speed"
\textcolor{blue}{ }

\item I don't really understand the procedure to find the drift velocity described here and fig. 7. What is $Nb_{max}$ e $Nb_{max/2}$? Why does $T_{max/2}$ correspond to $Nb_{max/2}$ and why is it used as $T_{max}$? If I make a quick calculation and use $T_{max}$ ~ 65 * 100ns and a drift length of ~ 3cm /cos(23°) ~ 7.5 cm I get a $v_{drift}$ ~ 1.15 cm/microsec << 5 cm/microsec which is the average value of drift velocity in drift chambers.
The procedure according to me would be:
- for each hit associated to a track, whose time information is available, take the drift time $t_{drift_{i}}$;
- plot the distribution of these $t_{drift_{i}}$;
- find the $T_{min}$ = minimum $t_{drift_{i}}$ and $T_{max}$ = maximum $t_{drift_{i}}$
- compute $delta_{t} = T_{max} - T_{min}$ and extract the drift velocity by dividing the track length / $delta_{t}$. Figure 8 would have the $delta_{t}$ instead of the $T_{max}$ vs z.
Please provide more details on the applied procedure, since I have the open questions I wrote before and I could not understand it properly. Moreover, please quote the value of the found drift velocity. Is it in accordance with the simulations?
\textcolor{blue}{ }

\item Figure 6: why are $T_{min}$ and $T_{max}$ not at the drift gap extremities?
\textcolor{blue}{ }

@@

\item line 306: "in one bin" should be explained better. I understood it is the subdivision in bins of the z coordinate, but it was not so obvious at the first reading
\textcolor{blue}{ }

\item Has the stability of the drift path been counterchecked with simulations varying the field according to the cathode radius variation? How much is the field variation if the radius have some mm of uncertainty?
\textcolor{blue}{ }

        /paragraph 4.3
\item The gain calibration is very quick. I would like more details, e.g. "setting the simulation properly" intends only GEANT4 or also MAGBOLTZ or GARFIELD? Were they used to simulate the drift and avalanche formation of the electrons? And the diffusion from the gas? Was a specific code written to simulate the electronics?
\textcolor{blue}{ }

\item line 330: "correction factors" are mentioned. On what? Why haven't only good tracks been used for calibration? Lack of statistics?
\textcolor{blue}{ }

\item When it says that the pad charge is "compared" to the neighboring ones, what happens next? Is it the noise reduction step described later? If so, please write it. 
\textcolor{blue}{ }

\item Figure 11: I don't understand it. How many tracks does the histo contain? If the single pad has 128 channels, how many channels does the single bin contain? Moreover, is the dE calculated on pad by pad basis? In that case, why don't you put just one point in the histo for each pad? What is the mean number of channels or pads fired by one track? Sorry for the list of questions, but I could not understand the figure.
\textcolor{blue}{ }

\item Figure 12 - please, put if after figure 11. Moreover, please change dEdx to dE/dx on y axis. Why are the left and right pictures so different? Talking about the deuteron band which is present only in the left figure and the smear on the top part of the right picture. 
\textcolor{blue}{ }

\subsection*{ Chapter 5}
	/paragraph 5.1	
\item Please detail a little bit more the procedure to remove the oscillatory noise. It says "event by event and channel by channel": if the ADC threshold is passed then a noise level is subtracted? If so, how is it calculated?
\textcolor{blue}{ } 
        /paragraph 5.2
\item How was "10.5 mm" cut chosen? is it in xy plane or in 3-dimensions?
\textcolor{blue}{ }

\item How was the "10 hits" cut chosen? What is the mean number of primary ionization in this gas mixture?
\textcolor{blue}{ }

\item < dE/dx > is computed here as corrected Etot divided total track length. Usually the mean dE/dx is computed with the truncated mean of the specific energy losses of each hit. Isn't it possible to compute it like this here? dx for each hit can be (maybe) computed from the difference in the hit times. Sum $dE_{i}$/Sum $dx_{i}$ is not equal to Sum ($dE_{i}/dx_{i}$).
\textcolor{blue}{ }

\subsection*{ Chapter 6}
	/paragraph 6.2
\item I understand that efficiency is a ratio between two integrals, each integral being the area of the Gaussian which fits the recoil mass distribution in the inclusive and exclusive case. If so, would it be possible to please draw both fits on the figure 14 and provide the integrals to compute the mean efficiency? If I misunderstood, please comment.
\textcolor{blue}{ }

\subsection*{ Chapter 7} 
\item Is it "high rate environment" or "high readout rate"? They are connected, but what is the rate the RTPC underwent during data taking?
\textcolor{blue}{ }

\item I understand the resolution and efficiency have been evaluated with the 2 GeV electrons. Is it foreseen to analyze also the 6 GeV electron runs, which were the actual data taking? Is there an evaluation of the foreseen RTPC performances in that case?
\textcolor{blue}{ }

----------------------------------------------
\subsection*{ Some general remarks on the layout}

\item I would add to the keywords also GEM or gas electron multipliers or multi pattern gas detectors (it depends on what is available).
\textcolor{blue}{ }

\item Please put the units on the axis of every figure, together with the physical quantity. In some figures it is only written in the caption or in the text.
\textcolor{blue}{ }

\item Sometimes to explain the dimension of something something like "250 mm long" (line 67) while some other times "84-mm-long" (on line 83) is written. Please make this uniform in the whole text (I just quoted two examples, but there are more in the text).
\textcolor{blue}{ }

\item In footnote 2, BoNuS is written BONUS and somewhere else in the text also BoNus. Please uniform this to the correct one, which I think is BoNuS.
\textcolor{blue}{ }

\item Please make the bibliography entries uniform: they are not all written with the same layout.
\textcolor{blue}{ }

@@

\item line 17: "GeV" --> "GeV/c"
\textcolor{blue}{ }

\item line 26: "nuclei" --> "nucleus"
\textcolor{blue}{ }

\item line 40: "to track" --> "to bend tracks"(since the magnetic field just bends the track and then the detector tracks them)
\textcolor{blue}{ }

\item line 91: "second gap" --> "second gas gap"
\textcolor{blue}{ }

\item line 110: "from the GEMs" -->  something like "after they have been multiplied by the GEMs" or "induced in the last gas gap" since the GEM is the amplification system.
\textcolor{blue}{ }

\item line 131: "axial magnetic field" --> "solenoidal magnetic field"
\textcolor{blue}{ }

\item line 133: "challenge" --> "challenges"
\textcolor{blue}{ }

\item line 133-134: "radial TPC" it would be better to uniform the way to write it in the whole text (like, "RTPC")
\textcolor{blue}{ }

\item line 167: "stage" --> "stages"
\textcolor{blue}{ }

\item line 176: "ReadOut" should always be written in the same way (see line 168) unless this was specifically written in a different way in the cited articles
\textcolor{blue}{ }

\item line 208: cm$^{-1}$ . s$^{-1}$ --> cm$^{-1}$ cdot s$^{-1}$ (the dot is not in the center vertically)
\textcolor{blue}{ }

\item line 208 again: "6.067" before it said "6.064", please fix the wrong one
\textcolor{blue}{ }

\item line 263: "2\%" --> I would put "around 2\%"
\textcolor{blue}{ }

\item line 268: "reconstructions" --> "reconstruction"
\textcolor{blue}{ }

\item line 269: "Paths" --> "Path"
\textcolor{blue}{ }

\item line 308: "codes" --> "code"
\textcolor{blue}{ }

\item line 405: "electron's" --> "electron"
\textcolor{blue}{ }

\item fig14 - caption: "W distribution" --> I would put "recoil mass W distribution"
\textcolor{blue}{ }

\item table 1: $sigma_{p}$ is actually $sigma_{p/p}$, since it is in percentage
\textcolor{blue}{ }

\item line 432: "Helium-4" --> "4He" (for uniformity, as was written before)
\textcolor{blue}{ }

\item line 488: There is an extra "," at the beginning of the item
\textcolor{blue}{ }

The topic of the article is interesting but I would recommend a revision. Please I would like the authors to address the questions asked and provide the required changes or explain why they think those changes are not necessary/correct. Thank you. Best regards.

\end{enumerate}

>>>>

\section*{Reviewers' comments (Oct. 11th, 2017)}

@@

Summary: the article describes the layout, operation and performances of a 
Radial Time Projection Chamber with the electron amplification stage provided 
by three layers of GEM. The main novelty is the application of the electron 
multiplier for the amplification stage in a TPC on a semi-cylindrical shaped 
plane. The detector, originally built for the BoNuS experiment, is in fact 
formed by two semi-cylindrically shaped halves connected together, with the 
axis coincident with the beam line.\\

The detector was implemented to measure DVCS of electrons on different light 
nuclei and the performances were evaluated on electron-$^4$He elastic 
scattering runs.\\

Chapter 1 describes the CLAS@JLab detector, inside which the RTPC was installed 
and took data. Chapter 2 focuses on the RTPC mechanical and electrical layout.  
From inner to outer, there are: the $^4$He gas target, a $^4$He gas gap, the 
actual time projection chamber. The time projection chamber is a 200~mm long 
detector composed by different gas gaps limited by concentric electrodes around 
the axis: cathode (R= 30~mm), G1(R= 60~mm), G2(R= 63~mm), G3(R= 66~mm), readout 
plane (R= 69~mm). Everything fits inside a 5T solenoidal magnetic field. It 
provides both time and charge measurements. Chapter 3 is a short description of 
the electronics and readout, mainly inherited from ALICE and BoNuS. The 
improvement stands in the higher readout rate capability. Chapter 4 talks about 
calibration of drift velocity, drift paths and energy loss measurements by the 
usage of simulations with MAGBOLTZ and tuning the results on elastic scattering 
data. Chapter 5 concentrates on track finding/fitting procedure and noise 
evaluation and subtraction. Chapter 6 reports on resolution and efficiency from 
the elastic scattering reconstruction of 1 GeV electrons on 4He and Chapter 7 
concludes the paper.\\

The article main points of interest are the followings:

a) The usage of GEMs as avalanche creators inside the time projection chamber.  
As far as I know other TPC with the wires substituted by GEM layers have been 
(or are being) realized, like ALICE TPC upgrade or the FOPI one (proposed for 
PANDA), but in those cases the GEM are planar and on the end plane of the TPC, 
not around the beamline.

b) The shaping of the GEM foils around the target. However, since now a fully 
cylindrical GEM foil has been realized (for the KLOE-2 detector and for the 
next BESIII inner tracker) I would not call these "cylindrical" GEMs, but 
"semi-cylindrical" GEMs to point out the difference (which reflects in the 
construction procedure). Maybe these other experiments using GEMs should be 
mentioned due to the similarities, thought they are successive in time to this 
RTPC construction.\\

Concerning the work description, it is mainly exhaustive, but in some points 
there are open questions that I would like to submit to the authors in the 
following.

\newpage
\section*{Chapter by chapter comments}

@@

\subsection*{Chapter 2}
\item As already said I would not speak of cylindrical GEMs but 
   semi-cylindrical. Moreover, please add the reference to Sauli's paper [11] 
   when speaking the first time about GEM in the text.\\
\textcolor{blue}{ }

\item In my opinion, this chapter should highlight better which are the 
   improvements w.r.t. BoNuS detector to underline the originality of this 
   work. For example, better acceptance? Higher gain? Higher electric 
   stability? Lower material budget? Please quote some old and new values, 
   maybe in a table, to make them evident.\\
\textcolor{blue}{ }

\item Relevant length and thicknesses of the various elements are reported in 
   the text and in the figure, can you please add also the z position of the 
   target w.r.t the detector? To give the complete information, I would also 
   add the value of the induction gap electric field, which is the only missing 
   field value and the value of the reached amplification gain with the three 
   GEM.\\
\textcolor{blue}{ }

\item When speaking of low spark rate the reference [12] is quoted, which is 
   the PDG. Maybe it is better to quote more specific studies like the ones by 
   Bachmann et al.\\
\textcolor{blue}{ }

\item line 119: is the Kapton of the GEM foil really 300 mum thick? It is 
   usually very thin, like 50 mum, in order to have low material budget and 
   very high fields.\\
\textcolor{blue}{ }

\subsection*{ Chapter 3}
\item The description of the electronics looks to me a little not well 
   organized, like a collection of info from previous descriptions from ALICE 
   and BoNuS. It is a series of details, some of which not really relevant for 
   the good understanding of the work described in the paper. So, I would put 
   only some general info (the number of channels/pad, the number of time 
   samples and their width for each channel and the number of  ADC samples and 
   their width for each channel) with the reference where to find more material 
   and just write explicitly the novelties, such as the fact that the 
   acquisition rate was increased (footnote 2).\\
\textcolor{blue}{ }

\item Also, I understand that fig. 5 comes from reference [14], updated with 
   the values of the RTPC instead of the ALICE-TPC, but it seems to me that 
   there are some parts of the picture which have to be fixed. I list them 
   here:\\
- why does it say 768 pads?\\
- why 7.6 microsec?\\
- the anode wire e grid make no sense here\\
- why L1 and L2 (trigger levels?) \\
\textcolor{blue}{ }

\subsection*{ Chapter 4}
	/paragraph 4.1
\item I would really prefer to call it drift "velocity" instead of drift 
   "speed"\\
\textcolor{blue}{ }

\item I don't really understand the procedure to find the drift velocity 
   described here and fig. 7. What is $Nb_{max}$ e $Nb_{max/2}$? Why does 
   $T_{max/2}$ correspond to $Nb_{max/2}$ and why is it used as $T_{max}$? If I 
   make a quick calculation and use $T_{max}$ ~ 65 * 100ns and a drift length 
   of ~ 3cm /cos(23°) ~ 7.5 cm I get a $v_{drift}$ ~ 1.15 cm/microsec << 5 
   cm/microsec which is the average value of drift velocity in drift 
   chambers.\\
The procedure according to me would be:\\
- for each hit associated to a track, whose time information is available, take 
the drift time $t_{drift_{i}}$;\\
- plot the distribution of these $t_{drift_{i}}$;\\
- find the $T_{min}$ = minimum $t_{drift_{i}}$ and $T_{max}$ = maximum 
$t_{drift_{i}}$\\
- compute $delta_{t} = T_{max} - T_{min}$ and extract the drift velocity by 
dividing the track length / $delta_{t}$. Figure 8 would have the $delta_{t}$ 
instead of the $T_{max}$ vs z.\\
Please provide more details on the applied procedure, since I have the open 
questions I wrote before and I could not understand it properly. Moreover, 
please quote the value of the found drift velocity. Is it in accordance with 
the simulations?\\
\textcolor{blue}{ }

\item Figure 6: why are $T_{min}$ and $T_{max}$ not at the drift gap 
   extremities?\\
\textcolor{blue}{ }

@@

\item line 306: "in one bin" should be explained better. I understood it is the 
   subdivision in bins of the z coordinate, but it was not so obvious at the 
   first reading\\
\textcolor{blue}{ }

\item Has the stability of the drift path been counterchecked with simulations 
   varying the field according to the cathode radius variation? How much is the 
   field variation if the radius have some mm of uncertainty?\\
\textcolor{blue}{ }

        /paragraph 4.3
\item The gain calibration is very quick. I would like more details, e.g. 
   "setting the simulation properly" intends only GEANT4 or also MAGBOLTZ or 
   GARFIELD? Were they used to simulate the drift and avalanche formation of 
   the electrons? And the diffusion from the gas? Was a specific code written 
   to simulate the electronics?\\
\textcolor{blue}{ }

\item line 330: "correction factors" are mentioned. On what? Why haven't only 
   good tracks been used for calibration? Lack of statistics?\\
\textcolor{blue}{ }

\item When it says that the pad charge is "compared" to the neighboring ones, 
   what happens next? Is it the noise reduction step described later? If so, 
   please write it. \\
\textcolor{blue}{ }

\item Figure 11: I don't understand it. How many tracks does the histo contain? 
   If the single pad has 128 channels, how many channels does the single bin 
   contain? Moreover, is the dE calculated on pad by pad basis? In that case, 
   why don't you put just one point in the histo for each pad? What is the mean 
   number of channels or pads fired by one track? Sorry for the list of 
   questions, but I could not understand the figure.\\
\textcolor{blue}{ }

\item Figure 12 - please, put if after figure 11. Moreover, please change dEdx 
   to dE/dx on y axis. Why are the left and right pictures so different? 
   Talking about the deuteron band which is present only in the left figure and 
   the smear on the top part of the right picture. \\
\textcolor{blue}{ }

\subsection*{ Chapter 5}
        /paragraph 5.1	\item Please detail a little bit more the procedure to 
           remove the oscillatory noise. It says "event by event and channel by 
           channel": if the ADC threshold is passed then a noise level is 
           subtracted? If so, how is it calculated?\\
\textcolor{blue}{ }

/paragraph 5.2
\item How was "10.5 mm" cut chosen? is it in xy plane or in 3-dimensions?\\
\textcolor{blue}{ }

\item How was the "10 hits" cut chosen? What is the mean number of primary 
   ionization in this gas mixture?\\
\textcolor{blue}{ }

\item < dE/dx > is computed here as corrected Etot divided total track length. 
   Usually the mean dE/dx is computed with the truncated mean of the specific 
   energy losses of each hit. Isn't it possible to compute it like this here? 
   dx for each hit can be (maybe) computed from the difference in the hit 
   times. Sum $dE_{i}$/Sum $dx_{i}$ is not equal to Sum ($dE_{i}/dx_{i}$).\\
\textcolor{blue}{ }

\subsection*{ Chapter 6}

        /paragraph 6.2
\item I understand that efficiency is a ratio between two integrals, each 
   integral being the area of the Gaussian which fits the recoil mass 
   distribution in the inclusive and exclusive case. If so, would it be 
   possible to please draw both fits on the figure 14 and provide the integrals 
   to compute the mean efficiency? If I misunderstood, please comment.\\
\textcolor{blue}{ }

\subsection*{ Chapter 7} \item Is it "high rate environment" or "high readout 
   rate"? They are connected, but what is the rate the RTPC underwent during 
   data taking?\\
\textcolor{blue}{ }

\item I understand the resolution and efficiency have been evaluated with the 2 
   GeV electrons. Is it foreseen to analyze also the 6 GeV electron runs, which 
   were the actual data taking? Is there an evaluation of the foreseen RTPC 
   performances in that case?\\
\textcolor{blue}{ }

\subsection*{ Some general remarks on the layout}

\item I would add to the keywords also GEM or gas electron multipliers or multi 
   pattern gas detectors (it depends on what is available).\\
\textcolor{blue}{Updated}

\item Please put the units on the axis of every figure, together with the 
   physical quantity. In some figures it is only written in the caption or in 
   the text.\\
\textcolor{blue}{ }

\item Sometimes to explain the dimension of something something like "250 mm 
   long" (line 67) while some other times "84-mm-long" (on line 83) is written. 
   Please make this uniform in the whole text (I just quoted two examples, but 
   there are more in the text).\\
\textcolor{blue}{Updated everywhere}

\item In footnote 2, BoNuS is written BONUS and somewhere else in the text also 
   BoNus. Please uniform this to the correct one, which I think is BoNuS.\\
\textcolor{blue}{Updated to BoNuS everywhere}

\item Please make the bibliography entries uniform: they are not all written 
   with the same layout.\\
\textcolor{blue}{Updated}

@@

\item line 17: "GeV" --> "GeV/c"\\
\textcolor{blue}{Corrected}

\item line 26: "nuclei" --> "nucleus"\\
\textcolor{blue}{Corrected}

\item line 40: "to track" --> "to bend tracks"(since the magnetic field just 
   bends the track and then the detector tracks them)\\
\textcolor{blue}{Added}

\item line 91: "second gap" --> "second gas gap"\\
\textcolor{blue}{Added}

\item line 110: "from the GEMs" -->  something like "after they have been 
   multiplied by the GEMs" or "induced in the last gas gap" since the GEM is 
   the amplification system.\\
\textcolor{blue}{Added}

\item line 131: "axial magnetic field" --> "solenoidal magnetic field"\\
\textcolor{blue}{Replaced}

\item line 133: "challenge" --> "challenges"\\
\textcolor{blue}{Added}

\item line 133-134: "radial TPC" it would be better to uniform the way to write 
   it in the whole text (like, "RTPC")\\
\textcolor{blue}{Uniformed}

\item line 167: "stage" --> "stages"\\
\textcolor{blue}{Corrected}

\item line 176: "ReadOut" should always be written in the same way (see line 
   168) unless this was specifically written in a different way in the cited 
   articles\\
\textcolor{blue}{Uniformed}

\item line 208: cm$^{-1}$ . s$^{-1}$ --> cm$^{-1}$ cdot s$^{-1}$ (the dot is 
   not in the center vertically)\\
\textcolor{blue}{Corrected}

\item line 208 again: "6.067" before it said "6.064", please fix the wrong one
\textcolor{blue}{Corrected. It is 6.064} \\

\item line 263: "2\%" --> I would put "around 2\%"\\
\textcolor{blue}{Added}

\item line 268: "reconstructions" --> "reconstruction"\\
\textcolor{blue}{Corrected }

\item line 269: "Paths" --> "Path"\\
\textcolor{blue}{Corrected}

\item line 308: "codes" --> "code"\\
\textcolor{blue}{Corrected}

\item line 405: "electron's" --> "electron"\\
\textcolor{blue}{Corrected}

\item fig14 - caption: "W distribution" --> I would put "recoil mass W 
   distribution"\\
\textcolor{blue}{Added}

\item table 1: $sigma_{p}$ is actually $sigma_{p/p}$, since it is in 
   percentage\\
\textcolor{blue}{Yes it is. Corrected }

\item line 432: "Helium-4" --> "4He" (for uniformity, as was written before)\\
\textcolor{blue}{Changed to $^4$He}

\item line 488: There is an extra "," at the beginning of the item\\
\textcolor{blue}{Cleaned}\\
~\\
\end{enumerate}

The topic of the article is interesting but I would recommend a revision.  
Please I would like the authors to address the questions asked and provide the 
required changes or explain why they think those changes are not 
necessary/correct. Thank you. Best regards.\\
